### 2021-08-10 newvariant.tex
bib

\bibliography{newvariant_abbv.bib}

>>>>

\begin{thebibliography}{10}

\bibitem{switzerland2021variant}
Althaus CL, Reichmuth M, Hodcroft E, Riou J, Schibler M, Eckerle I, Kaiser L,
  Suter F, Huber M, Trkola A, and others .
\newblock 2021 {Transmission of SARS-CoV-2 variants in Switzerland}.
\newblock \url{https://ispmbern.github.io/covid-19/variants/}.

\bibitem{davies2021estimated}
Davies NG, Abbott S, Barnard RC, Jarvis CI, Kucharski AJ, Munday JD, Pearson
  CAB, Russell TW, Tully DC, Washburne AD, and others .
\newblock 2021 {Estimated transmissibility and impact of SARS-CoV-2 lineage
  B.1.1.7 in England}.
\newblock {\em Science}.

\bibitem{di2021impact}
Di~Domenico L, Pullano G, Sabbatini CE, L{\'e}vy-Bruhl D, and Colizza V.
\newblock 2021 {Impact of January 2021 social distancing measures on SARS-CoV-2
  B. 1.1. 7 circulation in France}.
\newblock {\em medRxiv}.
\newblock \url{https://www.medrxiv.org/content/10.1101/2021.02.14.21251708v1}.

\bibitem{graham2021changes}
Graham MS, Sudre CH, May A, Antonelli M, Murray B, Varsavsky T, Kl{\"a}ser K,
  Canas LS, Molteni E, and others .
\newblock 2021/05/03 2021 {Changes in symptomatology, reinfection, and
  transmissibility associated with the SARS-CoV-2 variant B.1.1.7: an
  ecological study}.
\newblock {\em Lancet Public Health}.
\newblock {\bfseries 6}, e335--e345.

\bibitem{leung2021early}
Leung K, Shum MH, Leung GM, Lam TT, and Wu~JT.
\newblock 2021 {Early transmissibility assessment of the N501Y mutant strains
  of SARS-CoV-2 in the United Kingdom, October to November 2020}.
\newblock {\em Euro Surveill.}
\newblock {\bfseries 26}, 2002106.

\bibitem{volz2021transmission}
Volz E, Mishra S, Chand M, Barrett JC, Johnson R, Geidelberg L, Hinsley WR,
  Laydon DJ, Dabrera G, O'Toole {\'A}, and others .
\newblock 2021 {Assessing transmissibility of SARS-CoV-2 lineage B.1.1.7 in
  England}.
\newblock {\em Nature}.

\bibitem{zhao2021}
Zhao S, Lou J, Cao L, Zheng H, Chong MKC, Chen Z, Chan RWY, Zee BCY, Chan PKS,
  and Wang MH.
\newblock 01 2021 {Quantifying the transmission advantage associated with N501Y
  substitution of SARS-CoV-2 in the UK: an early data-driven analysis}.
\newblock {\em J. Travel Med}.
\newblock taab011.

\bibitem{campbell2021increased}
Campbell F, Archer B, Laurenson-Schafer H, Jinnai Y, Konings F, Batra N, Pavlin
  B, Vandemaele K, Van~Kerkhove MD, Jombart T, and others .
\newblock 2021 Increased transmissibility and global spread of {SARS-CoV-2}
  variants of concern as at {June}, 2021.
\newblock {\em Euro Surveill.}
\newblock {\bfseries 26}, 2100509.

\bibitem{diekmann1990definition}
Diekmann O, Heesterbeek JAP, and Metz JA.
\newblock 1990 On the definition and the computation of the basic reproduction
  ratio $\mathcal{R}_0$ in models for infectious diseases in heterogeneous
  populations.
\newblock {\em J. Math. Biol.}
\newblock {\bfseries 28}, 365--382.

\bibitem{anderson1991infectious}
Anderson RM and May RM.
\newblock 1991 {\em {Infectious diseases of humans: dynamics and control}}.
\newblock Oxford University Press.

\bibitem{mills2004transmissibility}
Mills CE, Robins JM, and Lipsitch M.
\newblock 2004 Transmissibility of 1918 pandemic influenza.
\newblock {\em Nature}.
\newblock {\bfseries 432}, 904--906.

\bibitem{nishiura2009transmission}
Nishiura H, Castillo-Chavez C, Safan M, and Chowell G.
\newblock 2009 {Transmission potential of the new influenza A (H1N1) virus and
  its age-specificity in Japan}.
\newblock {\em Euro Surveill.}
\newblock {\bfseries 14}, 19227.

\bibitem{ma2014estimating}
Ma~J, Dushoff J, Bolker BM, and Earn DJD.
\newblock 2014 Estimating initial epidemic growth rates.
\newblock {\em Bull. Math. Biol.}
\newblock {\bfseries 76}, 245--260.

\bibitem{wallinga2007generation}
Wallinga J and Lipsitch M.
\newblock 2007 How generation intervals shape the relationship between growth
  rates and reproductive numbers.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 274}, 599--604.

\bibitem{svensson2007note}
Svensson {\AA}.
\newblock 2007 A note on generation times in epidemic models.
\newblock {\em Math. Biosci.}
\newblock {\bfseries 208}, 300--311.

\bibitem{fine2003interval}
Fine PE.
\newblock 2003 The interval between successive cases of an infectious disease.
\newblock {\em Am. J. Epidemiol.}
\newblock {\bfseries 158}, 1039--1047.

\bibitem{grassly2008mathematical}
Grassly NC and Fraser C.
\newblock 2008 Mathematical models of infectious disease transmission.
\newblock {\em Nat. Rev. Microbiol.}
\newblock {\bfseries 6}, 477--487.

\bibitem{britton2019estimation}
Britton T and Scalia~Tomba G.
\newblock 2019 {Estimation in emerging epidemics: Biases and remedies}.
\newblock {\em J. R. Soc. Interface}.
\newblock {\bfseries 16}, 20180670.

\bibitem{ali2020serial}
Ali ST, Wang L, Lau EH, Xu~XK, Du~Z, Wu~Y, Leung GM, and Cowling BJ.
\newblock 2020 {Serial interval of SARS-CoV-2 was shortened over time by
  nonpharmaceutical interventions}.
\newblock {\em Science}.
\newblock {\bfseries 369}, 1106--1109.

\bibitem{park2021forward}
Park SW, Sun K, Champredon D, Li~M, Bolker BM, Earn DJ, Weitz JS, Grenfell BT,
  and Dushoff J.
\newblock 2021 Forward-looking serial intervals correctly link epidemic growth
  to reproduction numbers.
\newblock {\em Proc. Natl. Acad. Sci. U.S.A.}
\newblock {\bfseries 118}, e2011548118.

\bibitem{lloyd2001realistic}
Lloyd AL.
\newblock 2001 Realistic distributions of infectious periods in epidemic
  models: changing patterns of persistence and dynamics.
\newblock {\em Theor. Popul. Biol.}
\newblock {\bfseries 60}, 59--71.

\bibitem{wearing2005appropriate}
Wearing HJ, Rohani P, and Keeling MJ.
\newblock 2005 Appropriate models for the management of infectious diseases.
\newblock {\em PLoS medicine}.
\newblock {\bfseries 2}, e174.

\bibitem{roberts2007model}
Roberts M and Heesterbeek J.
\newblock 2007 Model-consistent estimation of the basic reproduction number
  from the incidence of an emerging infection.
\newblock {\em J. Math. Biol.}
\newblock {\bfseries 55}, 803.

\bibitem{huber2016quantitative}
Huber JH, Johnston GL, Greenhouse B, Smith DL, and Perkins TA.
\newblock 2016 Quantitative, model-based estimates of variability in the
  generation and serial intervals of \textit{Plasmodium falciparum} malaria.
\newblock {\em Malaria journal}.
\newblock {\bfseries 15}, 1--12.

\bibitem{miller2010epidemics}
Miller JC, Davoudi B, Meza R, Slim AC, and Pourbohloul B.
\newblock 2010 Epidemics with general generation interval distributions.
\newblock {\em J. Theor. Biol.}
\newblock {\bfseries 262}, 107--115.

\bibitem{svensson2015influence}
Svensson {\AA}.
\newblock 2015 The influence of assumptions on generation time distributions in
  epidemic models.
\newblock {\em Math. Biosci.}
\newblock 270, 81--89.

\bibitem{park2019practical}
Park SW, Champredon D, Weitz JS, and Dushoff J.
\newblock 2019 A practical generation-interval-based approach to inferring the
  strength of epidemics from their speed.
\newblock {\em Epidemics}.
\newblock 27, 12--18.

\bibitem{eaton2014proportion}
Eaton JW and Hallett TB.
\newblock 2014 Why the proportion of transmission during early-stage {HIV}
  infection does not predict the long-term impact of treatment on {HIV}
  incidence.
\newblock {\em Proc. Natl. Acad. Sci. U.S.A.}
\newblock {\bfseries 111}, 16202--16207.

\bibitem{powers2014impact}
Powers KA, Kretzschmar ME, Miller WC, and Cohen MS.
\newblock 2014 Impact of early-stage {HIV} transmission on treatment as
  prevention.
\newblock {\em Proc. Natl. Acad. Sci. U.S.A.}
\newblock {\bfseries 111}, 15867--15868.

\bibitem{weitz2015modeling}
Weitz JS and Dushoff J.
\newblock 2015 Modeling post-death transmission of {Ebola}: challenges for
  inference and opportunities for control.
\newblock {\em Sci. Rep.}
\newblock {\bfseries 5}, 1--7.

\bibitem{park2020time}
Park SW, Cornforth DM, Dushoff J, and Weitz JS.
\newblock 2020 The time scale of asymptomatic transmission affects estimates of
  epidemic potential in the {COVID-19} outbreak.
\newblock {\em Epidemics}.
\newblock 31, 100392.

\bibitem{doi:10.1098/rspb.2020.1556}
Dushoff J and Park SW.
\newblock 2021 Speed and strength of an epidemic intervention.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 288}, 20201556.

\bibitem{kissler2021densely}
Kissler S, Fauver JR, Mack C, Tai CG, Breban MI, Watkins AE, Samant RM,
  Anderson DJ, Ho~DD, Grubaugh ND, and Grad YH.
\newblock 2021 {Densely sampled viral trajectories suggest longer duration of
  acute infection with B.1.1.7 variant relative to non-B.1.1.7 SARS-CoV-2}.
\newblock {\em medRxiv}.
\newblock \url{https://www.medrxiv.org/content/10.1101/2021.02.16.21251535v1}.

\bibitem{li2021viral}
Li~B, Deng A, Li~K, Hu~Y, Li~Z, Xiong Q, Liu Z, Guo Q, Zou L, Zhang H, and
  others .
\newblock 2021 {Viral infection and Transmission in a large well-traced
  outbreak caused by the Delta SARS-CoV-2 variant}.
\newblock {\em medRxiv}.
\newblock \url{https://www.medrxiv.org/content/10.1101/2021.07.07.21260122v1}.

\bibitem{zhang2021transmission}
Zhang M, Xiao J, Deng A, Zhang Y, Zhuang Y, Hu~T, Li~J, Tu~H, Li~B, Zhou Y, and
  others .
\newblock 2021 Transmission dynamics of an outbreak of the {COVID-19} {Delta}
  variant {B.1.617.2}--{Guangdong Province, China, May--June 2021}.
\newblock {\em China CDC Weekly}.
\newblock 3, 584--586.

\bibitem{goldstein2009reconstructing}
Goldstein E, Dushoff J, Ma~J, Plotkin JB, Earn DJ, and Lipsitch M.
\newblock 2009 Reconstructing influenza incidence by deconvolution of daily
  mortality time series.
\newblock {\em Proc. Natl. Acad. Sci. U.S.A.}
\newblock {\bfseries 106}, 21825--21829.

\bibitem{gostic2020practical}
Gostic KM, McGough L, Baskerville EB, Abbott S, Joshi K, Tedijanto C, Kahn R,
  Niehus R, Hay JA, De~Salazar PM, and others .
\newblock 12 2020 Practical considerations for measuring the effective
  reproductive number, $\mathcal{R}_t$.
\newblock {\em PLOS Comp. Biol.}
\newblock {\bfseries 16}, 1--21.

\bibitem{heesterbeek1996concept}
Heesterbeek J and Dietz K.
\newblock 1996 The concept of $\mathcal{R}_0$ in epidemic theory.
\newblock {\em Stat. Neerl.}
\newblock {\bfseries 50}, 89--110.

\bibitem{diekmann2000mathematical}
Diekmann O and Heesterbeek JAP.
\newblock 2000 {\em Mathematical epidemiology of infectious diseases: model
  building, analysis and interpretation}, volume~5.
\newblock John Wiley \& Sons.

\bibitem{roberts2004modelling}
Roberts M.
\newblock 2004 Modelling strategies for minimizing the impact of an imported
  exotic infection.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 271}, 2411--2415.

\bibitem{aldis2005integral}
Aldis G and Roberts M.
\newblock 2005 An integral equation model for the control of a smallpox
  outbreak.
\newblock {\em Math. Biosci.}
\newblock {\bfseries 195}, 1--22.

\bibitem{breda2012formulation}
Breda D, Diekmann O, De~Graaf W, Pugliese A, and Vermiglio R.
\newblock 2012 {On the formulation of epidemic models (an appraisal of Kermack
  and McKendrick)}.
\newblock {\em J. Biol. Dyn.}
\newblock {\bfseries 6}, 103--117.

\bibitem{champredon2018equivalence}
Champredon D, Dushoff J, and Earn DJ.
\newblock 2018 Equivalence of the {Erlang}-distributed {SEIR} epidemic model
  and the renewal equation.
\newblock {\em SIAM J. Appl. Math}.
\newblock {\bfseries 78}, 3258--3278.

\bibitem{fraser2007estimating}
Fraser C.
\newblock 2007 Estimating individual and household reproduction numbers in an
  emerging epidemic.
\newblock {\em PloS one}.
\newblock {\bfseries 2}.

\bibitem{champredon2015intrinsic}
Champredon D and Dushoff J.
\newblock 2015 Intrinsic and realized generation intervals in
  infectious-disease transmission.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 282}, 20152026.

\bibitem{champredon2018two}
Champredon D, Li~M, Bolker BM, and Dushoff J.
\newblock 2018 Two approaches to forecast {Ebola} synthetic epidemics.
\newblock {\em Epidemics}.
\newblock 22, 36--42.

\bibitem{kenah2008generation}
Kenah E, Lipsitch M, and Robins JM.
\newblock 2008 Generation interval contraction and epidemic data analysis.
\newblock {\em Math. Biosci.}
\newblock {\bfseries 213}, 71--79.

\bibitem{nishiura2010time}
Nishiura H.
\newblock 2010 Time variations in the generation time of an infectious disease:
  implications for sampling to appropriately quantify transmission potential.
\newblock {\em Math. Biosci. Eng.}
\newblock {\bfseries 7}, 851.

\bibitem{flaxman2020Rt}
Flaxman S, Mishra S, Gandy A, Unwin HJT, Mellan TA, Coupland H, Whittaker C,
  Zhu H, Berah T, Eaton JW, Monod M, and others .
\newblock 2020 {Estimating the effects of non-pharmaceutical interventions on
  COVID-19 in Europe}.
\newblock {\em Nature}.
\newblock {\bfseries 584}, 257--261.

\bibitem{moore2021vaccination}
Moore S, Hill EM, Tildesley MJ, Dyson L, and Keeling MJ.
\newblock 2021 {Vaccination and non-pharmaceutical interventions for COVID-19:
  a mathematical modelling study}.
\newblock {\em Lancet Infect. Dis.}
\newblock {\bfseries 21}, 793--802.

\bibitem{brauner2021inferring}
Brauner JM, Mindermann S, Sharma M, Johnston D, Salvatier J, Gaven{\v{c}}iak T,
  Stephenson AB, Leech G, Altman G, Mikulik V, and others .
\newblock 2021 {Inferring the effectiveness of government interventions against
  COVID-19}.
\newblock {\em Science}.
\newblock {\bfseries 371}.

\bibitem{doi:10.1098/rsif.2020.0144}
Park SW, Bolker BM, Champredon D, Earn DJD, Li~M, Weitz JS, Grenfell BT, and
  Dushoff J.
\newblock 2020 {Reconciling early-outbreak estimates of the basic reproductive
  number and its uncertainty: framework and applications to the novel
  coronavirus (SARS-CoV-2) outbreak}.
\newblock {\em J. R. Soc. Interface}.
\newblock {\bfseries 17}, 20200144.

\bibitem{ferretti2020quantifying}
Ferretti L, Wymant C, Kendall M, Zhao L, Nurtay A, Abeler-D{\"o}rner L, Parker
  M, Bonsall D, and Fraser C.
\newblock 2020 {Quantifying SARS-CoV-2 transmission suggests epidemic control
  with digital contact tracing}.
\newblock {\em Science}.
\newblock {\bfseries 368}.

\bibitem{leung2017monitoring}
Leung K, Lipsitch M, Yuen KY, and Wu~JT.
\newblock 2017 Monitoring the fitness of antiviral-resistant influenza strains
  during an epidemic: a mathematical modelling study.
\newblock {\em Lancet Infect. Dis.}
\newblock {\bfseries 17}, 339--347.

\bibitem{leung2020empirical}
Leung K, Pei Y, Leung GM, Lam TT, and Wu~JT.
\newblock 2020 {Empirical transmission advantage of the D614G mutant strain of
  SARS-CoV-2}.
\newblock {\em medRxiv}.
\newblock \url{https://www.medrxiv.org/content/10.1101/2020.09.22.20199810v1}.

\bibitem{wallinga2004different}
Wallinga J and Teunis P.
\newblock 2004 Different epidemic curves for severe acute respiratory syndrome
  reveal similar impacts of control measures.
\newblock {\em Am. J. Epidemiol.}
\newblock {\bfseries 160}, 509--516.

\bibitem{cori2013new}
Cori A, Ferguson NM, Fraser C, and Cauchemez S.
\newblock 2013 A new framework and software to estimate time-varying
  reproduction numbers during epidemics.
\newblock {\em Am. J. Epidemiol.}
\newblock {\bfseries 178}, 1505--1512.

\bibitem{abbott2020estimating}
Abbott S, Hellewell J, Thompson RN, Sherratt K, Gibbs HP, Bosse NI, Munday JD,
  Meakin S, Doughty EL, Chun JY, and others .
\newblock 2020 {Estimating the time-varying reproduction number of SARS-CoV-2
  using national and subnational case counts}.
\newblock {\em Wellcome Open Research}.
\newblock {\bfseries 5}, 112.

\bibitem{knight2020estimating}
Knight J and Mishra S.
\newblock 2020 {Estimating effective reproduction number using generation time
  versus serial interval, with application to COVID-19 in the Greater Toronto
  Area, Canada}.
\newblock {\em Infect. Dis. Model.}
\newblock 5, 889--896.

\bibitem{li2021temporal}
Li~Y, Campbell H, Kulkarni D, Harpur A, Nundy M, Wang X, Nair H, for COVID UN,
  and others .
\newblock 2021 {The temporal association of introducing and lifting
  non-pharmaceutical interventions with the time-varying reproduction number
  (R) of SARS-CoV-2: a modelling study across 131 countries}.
\newblock {\em Lancet Infect. Dis.}
\newblock {\bfseries 21}, 193--202.

\bibitem{tsang2020effect}
Tsang TK, Wu~P, Lin Y, Lau EH, Leung GM, and Cowling BJ.
\newblock 2020 {Effect of changing case definitions for COVID-19 on the
  epidemic curve and transmission parameters in mainland China: a modelling
  study}.
\newblock {\em The Lancet Public Health}.
\newblock {\bfseries 5}, e289--e296.

\bibitem{ukinvest}
{Public Health England} .
\newblock 2020 {Investigation of novel SARS-CoV-2 variant: Variant of Concern
  202012/01}.
\newblock
  \url{https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/959426/Variant_of_Concern_VOC_202012_01_Technical_Briefing_5.pdf}.

\bibitem{ganyani2020estimating}
Ganyani T, Kremer C, Chen D, Torneri A, Faes C, Wallinga J, and Hens N.
\newblock 2020 {Estimating the generation interval for coronavirus disease
  (COVID-19) based on symptom onset data, March 2020}.
\newblock {\em Euro Surveill.}
\newblock {\bfseries 25}, 2000257.

\bibitem{fraser2004factors}
Fraser C, Riley S, Anderson RM, and Ferguson NM.
\newblock 2004 Factors that make an infectious disease outbreak controllable.
\newblock {\em Proc. Natl. Acad. Sci. U.S.A.}
\newblock {\bfseries 101}, 6146--6151.

\bibitem{scarabel2021renewal}
Scarabel F, Pellis L, Ogden NH, and Wu~J.
\newblock 2021 A renewal equation model to assess roles and limitations of
  contact tracing for disease outbreak control.
\newblock {\em R. Soc. Open Sci.}
\newblock {\bfseries 8}, 202091.

\bibitem{unwin2020state}
Unwin HJT, Mishra S, Bradley VC, Gandy A, Mellan TA, Coupland H, Ish-Horowicz
  J, Vollmer MA, Whittaker C, Filippi SL, and others .
\newblock 2020 {State-level tracking of COVID-19 in the United States}.
\newblock {\em Nat. Commun.}
\newblock {\bfseries 11}, 1--9.

\bibitem{brett2020transmission}
Brett TS and Rohani P.
\newblock 2020 Transmission dynamics reveal the impracticality of {COVID-19}
  herd immunity strategies.
\newblock {\em Proc. Natl. Acad. Sci. U.S.A.}
\newblock {\bfseries 117}, 25897--25903.

\bibitem{Ferretti2020timing}
Ferretti L, Ledda A, Wymant C, Zhao L, Ledda V, Abeler-D{\"o}rner L, Kendall M,
  Nurtay A, Cheng HY, Ng~TC, and others .
\newblock 2020 The timing of {COVID-19} transmission.
\newblock {\em medRxiv}.
\newblock \url{https://www.medrxiv.org/content/10.1101/2020.09.04.20188516v2}.

\bibitem{abdool2021new}
Abdool~Karim SS and de~Oliveira T.
\newblock 2021 {New SARS-CoV-2 variants—clinical, public health, and vaccine
  implications}.
\newblock {\em N. Engl. J. Med.}

\bibitem{fontanet2021sars}
Fontanet A, Autran B, Lina B, Kieny MP, Karim SSA, and Sridhar D.
\newblock 2021 {SARS-CoV-2 variants and ending the COVID-19 pandemic}.
\newblock {\em Lancet}.
\newblock {\bfseries 397}, 952--954.

\bibitem{walensky2021sars}
Walensky RP, Walke HT, and Fauci AS.
\newblock 2021 {SARS-CoV-2 variants of concern in the United
  States---Challenges and opportunities}.
\newblock {\em JAMA}.
\newblock {\bfseries 325}, 1037--1038.

\bibitem{hellewell2020feasibility}
Hellewell J, Abbott S, Gimma A, Bosse NI, Jarvis CI, Russell TW, Munday JD,
  Kucharski AJ, Edmunds WJ, Sun F, and others .
\newblock 2020 {Feasibility of controlling COVID-19 outbreaks by isolation of
  cases and contacts}.
\newblock {\em Lancet Glob. Health}.
\newblock {\bfseries 8}, e488--e496.

\end{thebibliography}
